---
title: "SVM_Kernel"
author: "LEESUJAE"
date: "2018년 4월 8일"
Reference: Postech Mooc, Advanced R(LEE HE SEON)
output: html_document
---
###1. Read Data
```{r iris}
summary(iris)
attach(iris)
```

###2.Package install for SVM, e'1071', for crosstable, 'caret'
```{r packages}
install.packages(c("e1071","caret"))
library(e1071)
library(caret)
help(svm)
```

###3.Training & Test Data set 
```{r seed}
set.seed(1000)
N=nrow(iris)
tr.idx=sample(1:N, size=N*2/3, replace = F) #split data
y=iris[,5] #target variable
train=iris[tr.idx,] #training data
test=iris[-tr.idx,]
```

###4. Kernel type 별 SVM 실행
# degree: parameter needed for kernel of type polynomial (default: 3)
# gamma: parameter needed for all kernels except linear (default: 1/(data dimension))
# coef0: parameter needed for kernels of type polynomial and sigmoid (default: 0)
```{r kernel}
m1<-svm(Species~., data=train) #default 는 radial basis exp(-gamma*|u-v|^2)
summary(m1)

m2<-svm(Species~., data=train, kernel="polynomial") #(gamma*u'*v + coef0)^degree
summary(m2)

m3<-svm(Species~., data=train, kernel="sigmoid") #tanh(gamma*u'*v + coef0)
summary(m3)

m4<-svm(Species~., data=train, kernel="linear")
summary(m4)
```

###5. Prediction_Radial Basis Function
```{r prediction}
pred11<-predict(m1,test)
confusionMatrix(pred11, test$Species)#predict와 test Species와 비교, Accuracy 96%
```

###6. prediction_Polynomial Function
```{r polynomial}
pred12<-predict(m2, test)
confusionMatrix(pred12, test$Species)#Accuracy 90%
```

###7 prediction_sigmoid
```{r sigmod}
pred13<-predict(m3, test)
confusionMatrix(pred13, test$Species)#Accuracy 90%
```

###8. prediction_linear
```{r linear}
pred14<-predict(m4, test)
confusionMatrix(pred14,test$Species)#Accuracy 96%
```